### 2024-07-25 paper.tex
finish with the sl2-triple

\section{Slodowy slice}
A basis for \(\spl_2(\mathbb{C})\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (???).
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.
\par Let
\[e = \begin{pNiceArray}{ccccc}
 0 \\
    1 & 0 \\
  & 1 & \ddots \\
   & & \ddots & 0 \\
   &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
where there are \(n - 1\) ones.
We will find the Slodowy slice at \(e\).
\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i, i}\), that \(f_{1,2} = h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).

>>>>

\section{Slodowy slice}
A basis for \(\spl_2(\mathbb{C})\) is
\[e' := \begin{pmatrix}0 & 1 \\ 0 & 0 \\\end{pmatrix}, h' := \begin{pmatrix}1 & 0 \\0 & -1\end{pmatrix}, f' := \begin{pmatrix}0 & 0 \\1 & 0\end{pmatrix}.\]
Given a Lie algebra \(\mathfrak{g}\), and a homomorphism \(\phi : \spl_2 \to \mathfrak{g}\) sending \((e', h', f')\) to \((e, h, f)\), we say that \((e, h, f)\) is an \emph{\(\spl_2\)-triple}.
Observe that \(e, f\) must be nilpotent, and \(h\) must be Cartan (???).
If \(\mathfrak{g}\) is semisimple, then given any nilpotent \(e \in \mathfrak{g}\), the Jacobson-Morozov theorem \cite[3.7.1]{ehf} says that there exist \(h, f \in \mathfrak{g}\) such that \((e, h, f)\) is an \(\spl_2\)-triple.
\par Given \((e, h, f)\), we define the \emph{Slodowy slice at \(e\)} as \(\mathcal{S}_e := e + \ker \ad_f\).
By the Jacobson-Morozov theorem, we can always find a Slodowy slice at any nilpotent \(e \in \mathfrak{g}\), when \(\mathfrak{g}\) is semisimple.

\subsection{Finding an \(\spl_2\)-triple in a simple case}
\par Let
\[e = \begin{pNiceArray}{ccccc}
 0 \\
    1 & 0 \\
  & 1 & \ddots \\
   & & \ddots & 0 \\
   &   &  & 1 & 0
   \end{pNiceArray} \in \mathfrak{sl}_{n},\]
where there are \(n - 1\) ones.
We will find the Slodowy slice at \(e\).
\par As a first step, we will find an \(\spl_2\)-triple with \(e\) as its first element.
Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
From the first equation we find that
\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
\[\sum_i h_{ii} = 0.\]
This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
So we have determined \(h\); it is 
\[h = \begin{pmatrix}
    n - 1  & \\
    & n - 3 \\
    & & \ddots \\
    & & & 3 - n \\
    & & & & 1 - n 
\end{pmatrix}.\]
Now, we can use our expression for \(f\) in terms of \(h\) to obtain
\[f = \begin{pmatrix}
    0 & 1 - n \\
    & 0 & (1 - n) + (3 - n) \\
    & & \ddots & \ddots \\
    & & & 0 & (1 - n) + \cdots + (n - 1) \\
    & & & & 0
\end{pmatrix} = \]
\[\begin{pmatrix}
    0 & 1 (1 - n) \\
      & 0 & 2 (2 - n) \\
    & & 0 & (n - 2) (-2) \\
    & & & 0 & (n - 1) (-1)\\
    & &  & & 0
\end{pmatrix}.\]

\subsection{Finding an \(\spl_2\)-triple in a slightly less simple case}
Now, suppose \(e = \)
